Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-08-10 src/tex/ms.tex
Update ms.tex

\author{Thomas C.K. Ng}
\email{thomas.ng@link.cuhk.edu.hk}

@@

Since Einstein proposed his theory of general relativity (GR), it was tested in a wide range of length scales.
After a century, we know that GR do not agree with quantum theories at some length scale.
To unify both theories, we need to study the possibility of different beyond-GR theories.
Some beyond-GR theories such as Chern-Simons theory (CS) suggested that there is gravitational wave (GW) amplitude birefringence,
while GR predicts there is no birefringence.

GW amplitude birefringence is a property of space which consists of the enhancement of one GW polarisation over the other during the propagation of the wave.
To illustrate the property, \textbf{[use snapshot from the animation to explain both frequency-dependent and frequency-independent birefringence]}

@@

\begin{enumerate}
    \item Introduction
    \begin{enumerate}
        \item Motivation
        \begin{enumerate}
            \item GR broke down at some scale, find a new theory
            \item CS: beyond-GR theory
            \item test CS property (GW amplitude birefringence)
        \end{enumerate}
        \item Amplitude Birefringence
        \begin{enumerate}
            \item GW amplitude birefringence is a property of space
            \item birefringence: enhance one and suppress another
        \end{enumerate}
        \item Amplitude Ratio
        \begin{enumerate}
            \item GR: amplitude ratio depends on $\iota$ only
            \item nonGR: also depends on $\kappa$, $d_C$ and $f$
        \end{enumerate}
    \end{enumerate}
    \item Method
    \begin{enumerate}
        \item PE on GWTC-3 to constrain $\kappa$
        \item Assume GW are generated as GR described
        \item birefringence is considered during the propagation
        \item waveform modification
    \end{enumerate}
    \item Results
    \begin{enumerate}
        \item GW150914
        \begin{enumerate}
            \item figure with frequency-dependent and frequency-independent
            \item posterior from $\cos\iota$ looks different
            \item frequency-dependent: degeneracy between $\iota$ and $\kappa$
            \item frequency-independent: degeneracy broken and $\kappa$ near $0$
        \end{enumerate}
        \item GWTC-3
        \begin{enumerate}
            \item figure of $\kappa$ of all events
            \item constraint on $\kappa$
            \item improvement of constraint on $\kappa$ compare to previous studies
        \end{enumerate}
    \end{enumerate}
    \item Discussion
    \begin{enumerate}
        \item Limitation
        \begin{enumerate}
            \item orientation of detector (polarisations)
            \item sensitivity of detector
        \end{enumerate}
        \item Future Study
        \begin{enumerate}
            \item More events from detector
            \item Higher order terms
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

>>>>

\author{Thomas C.K. Ng}
\email{thomas.ng@link.cuhk.edu.hk}
\affiliation{Department of Physics and Institute of Theoretical Physics, The Chinese University of Hong Kong, Shatin, Hong Kong}

\author{Maximiliano Isi}
\email{misi@flatironinstitute.org}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, United States}

\author{Kaze W. K. Wong}
\email{kwong@flatironinstitute.org}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, United States}

\author{Will M. Farr}
\email{wfarr@flatironinstitute.org}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, United States}
\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook NY 11794, United States}

@@

Since Einstein proposed his theory of general relativity (GR), it was tested in a wide range of length scales.
After a century, we know that GR do not agree with quantum theories at some length scale.
To unify both theories, we need to study the possibility of different beyond-GR theories.
Some beyond-GR theories such as Chern-Simons theory (CS) suggested that there is gravitational wave (GW) amplitude birefringence,
while GR predicts there is no birefringence.
GW amplitude birefringence is a property of space which consists of the enhancement of one GW polarisation over the other during the propagation of the wave.

% To illustrate the effect of amplitude birefringence,
% the amplitudes of two polarisations of a artificial GW signal are shown in figure \textbf{[X]}.

@@

\begin{enumerate}
    \item Introduction
    \begin{enumerate}
        \item Motivation
        \begin{enumerate}
            \item GR broke down at some scale, find a new theory
            \item CS: beyond-GR theory
            \item test CS property (GW amplitude birefringence)
        \end{enumerate}
        \item Amplitude Birefringence
        \begin{enumerate}
            \item GW amplitude birefringence is a property of space
            \item birefringence: enhance one and suppress another
            \item figure to illustrate the effect of birefringence
        \end{enumerate}
        \item Amplitude Ratio
        \begin{enumerate}
            \item GR: amplitude ratio depends on $\iota$ only
            \item nonGR: also depends on $\kappa$, $d_C$ and $f$
        \end{enumerate}
    \end{enumerate}
    \item Method
    \begin{enumerate}
        \item PE on GWTC-3 to constrain $\kappa$
        \item Assume GW are generated as GR described
        \item birefringence is considered during the propagation
        \item waveform modification
    \end{enumerate}
    \item Results
    \begin{enumerate}
        \item GW150914
        \begin{enumerate}
            \item figure with frequency-dependent and frequency-independent
            \item posterior from $\cos\iota$ looks different
            \item frequency-dependent: degeneracy between $\iota$ and $\kappa$
            \item frequency-independent: degeneracy broken and $\kappa$ near $0$
        \end{enumerate}
        \item GWTC-3
        \begin{enumerate}
            \item figure of $\kappa$ of all events
            \item constraint on $\kappa$
            \item improvement of constraint on $\kappa$ compare to previous studies
        \end{enumerate}
    \end{enumerate}
    \item Discussion
    \begin{enumerate}
        \item Limitation
        \begin{enumerate}
            \item orientation of detector (polarisations)
            \item sensitivity of detector
        \end{enumerate}
        \item Future Study
        \begin{enumerate}
            \item More events from detector
            \item Higher order terms
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
